---
title: "Amandafw_OriginalHomeworkCode_01"
author: "Amanda Wu"
date: "2023-09-14"
output: 
  prettydoc::html_pretty:
    theme: cayman
    highlight: vingette
---


### Challenge 1
```{r Challenge 1}
##Module 4 Challenge 1
#First, create a vector of 1, word character strings comprising the first line of the novel Ulysses, by James Joyce: “Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed.”
#Then, extract every third element of this vector.

Ulysses <- c("Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed.") #made a string with the sentence
Ulysses
c <- (strsplit(Ulysses, " ",)[[1]]) #used strsplit to split each word between a space into each different substrings 
c
f <- c[seq(from = 3, to = 22, by = 3)] #used seq to take the third word 
f
```

### Challenge 2
```{r Challenge 2}
m <- matrix(data = 1:80, nrow = 8, ncol = 10, byrow = FALSE) #made the matrix following Module 4
m
#Given the matrix, m, above, extract the 2nd, 3rd, and 6th columns and assign them to the variable x
x <- m[, c(2,3,6)] #the numbers after the comma represents columns 
x
#Given the matrix, m, above, extract the 6th to 8th row and assign them to the variable x
r <- c(6,7,8) #specifies the rows
x <- m[r, , drop = FALSE] 
x
#Given the matrix, m, above, extract the elements from row 2, column 2 to row 6, column 9 and assign them to the variable x
r <- c(2)
x <- m[, c(2:6, 9)][r, , drop = FALSE]
x
#or?
x <- m[2, c(2:6, 9)]
x
#not sure which one is correct
```

### Challenge 3
```{r Challenge 3}
#Construct a 4-dimensional, 400 element array (5 x 5 x 4 x 4) named a consisting of the numbers 400 to 1 (i.e., a descending series)
a <- array(400:1, dim = c(5, 5, 4, 4)) #followed the steps in Module 4 making an array but 400:1 because it is in descending order 
a
b <- a[1, 1, 1, 2] 
b
c <- a[2, 3, 2, ]
c
d <- a[1:5, 1:5, 3, 3]
d
```

### Challenge 4
```{r Challenge 4}
#Create a list representing this (simplified) primate taxonomy: 
#Ex:
Lemuroidea <- c("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae",
    "Daubentoniidae")
Lorisoidea <- c("Lorisidae", "Galagidae")
Strepsirhini <- list(Lemuroidea, Lorisoidea)
names(Strepsirhini) <- list("Lemuroidea", "Lorisoidea")
Strepsirhini

Platyrrhini <- c("Cebidae", "Atelidae", "Pitheciidae") #constructed the lists following the example
Catarrhini <- c("Cercopithecidae", "Hylobatidae", "Hominidae")
Anthropoidea <- list(Platyrrhini, Catarrhini)
names(Anthropoidea) <- list("Platyrrhini", "Catarrhini")
Anthropoidea

Tarsioidea <- c("Tarsiidae")
Tarsioidea
Haplorhini <- list(Anthropoidea, Tarsioidea)
names(Haplorhini) <- c("Anthropoidea", "Tarsioidea")
Haplorhini

Primates <- list(Haplorhini, Strepsirhini)
names(Primates) <- list("Haplorhini", "Strepsirhini")
Primates 

#Question: Are the names supposed to stack as you go down the list? Ex: $Strepsirhini$Lemuroidea 
```

### Challenge 5
```{r Challenge 5}
#Store the following numbers as a 5 x 3 matrix, called “m3”: 3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2. Be sure to fill the matrix ROW-WISE
x <- c(3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2) #made a vector
m3 <- matrix(x, nrow = 5, ncol = 3, byrow = TRUE) #made a matrix with 5 rows and 3 columns organized by row
m3
#Coerce the matrix to a data frame.
df <- data.frame(m3) 
df
#As a data frame, coerce the second column to be logical-valued
logic <- as.logical(df$X2) #included the $ because it wouldn't work without it
logic
#As a data frame, coerce the third column to be factor-valued
factor <- as.factor(df$X3)
factor
#Use the str() command to show the data type for each variable in your dataframe.
str(df)
str(logic)
str(factor)
#Questionable whether this is what the instructions were asking for
```


## Troubleshooting Tips/Errors: 
* Module 3: Step 4 error "remote origin already exists." (fixed)
  + Go to terminal and enter: git remote remove origin
  + To check that handler is deleted properly, run the following: git remote -v
  + Enter the desired origin from code in github


* Module 4 Challenge 1 TIP: 
  + Str_split will take a string and divide it into substrings but make sure that simplify is TRUE or else it may not work


* Module 5 Errors:
  + unable to install XLConnect
    + Error message: Error: package or namespace load failed for ‘XLConnect’:
 .onLoad failed in loadNamespace() for 'rJava', details:
  call: dyn.load(jli, FALSE)
  error: unable to load shared object '/Library/Internet Plug-Ins/JavaAppletPlugin.plugin/Contents/Home/lib/jli/libjli.dylib':
  dlopen(/Library/Internet Plug-Ins/JavaAppletPlugin.plugin/Contents/Home/lib/jli/libjli.dylib, 0x000A): tried: '/Library/Internet Plug-Ins/JavaAppletPlugin.plugin/Contents/Home/lib/jli/libjli.dylib' (mach-o file, but is an incompatible architecture (have 'x86_64', need 'arm64e'))

  + unable to enter "drop_auth()"
    + Error message: Error in oauth2.0_access_token(endpoint, app, code = code, user_params = user_params,  : 
  Bad Request (HTTP 400). Failed to get an access token.


